Coherent optical association of a single molecule

### 2020-09-24 paper.tex
Update on Overleaf.

Pioneering experiments used weakly bound molecular excited states in the Raman transition to en Raman Rabi frequency, but such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.

>>>>

Pioneering experiments used weakly bound molecular excited states in the Raman transition to ensure a large Raman Rabi frequency, but such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
